Elicitation Complexity via Convex Piecewise Linear Loss Functions

### 2018-11-12 jessie-writeup/jw-holes-carified.tex
Tidied up proof of Conjecture 1

\begin{definition}
Let $\Gamma:\P\toto\R$.
Define $\text{strip}(\Gamma) := \{ \Gamma_r : r \in \R \}$.
\end{definition}
Informally, strip removes labels from the property.
\btw{Note: Strip includes the boundaries of level sets / lower dimensional level sets.}

@@

Observe that for every set of properties $\gamma: \P \toto \R'$ and $\zeta: \P \toto \R$ such that $\gamma \approx \zeta$, there is a bijection $\phi:\R' \to \R$ so that $\phi(\gamma(p)) = \zeta(p)$ \footnote{Here, we slightly abuse notation and, given the finite set $S$, write $\phi(S) := \{\phi(x) : x \in S \}$.	($\phi$ is real valued, but we might be taking $\phi$ on every element of a set.)} for all $p \in \P$.

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma:\P \toto \reals^d$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R$ such that $\gamma \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets}

	Construct the finite set $\R' = \{r \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$. \jessie{(HOLE)- Check this is how we want to state the construction of $\R'$.}
	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.
	As $\Gamma$ is nondegenerate, there is some report $r \in \reals^d$ such that $r \in \Gamma(p)$.
	For every $p \in \P$, there is some level set $\theta$ so that $p \in \cl{\theta}$, and since level sets of elicitable properties are closed (see Lemma~\ref{lem:closed-level-sets}), and therefore $p \in \theta$.
	Thus there is some report $r \in \R'$ so that $r \in \gamma(p)$, so $\gamma$ is nondegenerate.

	\jessie{This next paragraph is definitely incomplete (HOLE)}
	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
	Any level set with a redundant report must either (a.) equal to another level set or (b.) a proper subset of another level set. 
	However, in our preliminary step of removing redundant reports in $\reals^d$ in defining $\R$, we know that (a.) does not happen.
	To see that (b.) does not happen, consider that a level set of an elicitable property is a proper subset 
	\jessie{End the hole here}

	Therefore, there will be at least one $r \in \R'$ per distribution, and since level sets are closed, $\gamma$ will still be nondegenerate.
	Therefore, our constructed $\gamma$ is nondegenerate, nonredundant, and $\gamma \preceq \Gamma$.

>>>>

\begin{definition}
Let $\Gamma:\P\toto\R$.
Define $\text{strip}(\Gamma) := \{ \Gamma_r : r \in \R \}$.
\end{definition}
Informally, strip removes labels from the property.
\btw{Strip includes the boundaries of level sets / lower dimensional level sets.}

@@

Observe that for every set of properties $\gamma: \P \toto \R'$ and $\zeta: \P \toto \R$ such that $\gamma \approx \zeta$, there is a bijection $\phi:\R' \to \R$ so that $\phi(\gamma(p)) = \zeta(p)$ \footnote{Here, we slightly abuse notation and, given the finite set $S$, write $\phi(S) := \{\phi(x) : x \in S \}$.	($\phi$ is real valued, but we might be taking $\phi$ on every element of a set.)} for all $p \in \P$.
\jessie{In hindsight-- not sure on this because of the extra dimension embedding counter example...}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma:\P \toto \R$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets}

	Construct the finite set $\R' = \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$, where $[r]$ is one consistent report for all the reports $r, r'$ so that $\Gamma_r = \Gamma_{r'}$. 
	\jessie{(HOLE)-- double check/clarify the construction of $\R'$.}
	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.
	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
	For every $p \in \P$, there is some level set $\theta$ so that $p \in \cl{\theta} = \theta$, since level sets of elicitable properties are closed (see Lemma~\ref{lem:closed-level-sets}).
	Thus there is some report $r \in \R'$ so that $r \in \gamma(p) = \Gamma(p) \cap \R'$, so $\gamma$ is nondegenerate.

	\jessie{This next paragraph is definitely incomplete (HOLE)}
	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
	Any level set with a redundant report must either (a.) equal to another level set or (b.) a proper subset of another level set. 
	We know that (a.) does not happen from the construction of $\R'$ using only one equivalent report per level set.
	To see that (b.) does not happen, suppose for contradiction that $r_1, r_2 \in \R'$ so that $\gamma_{r_1}\subsetneq \gamma_{r_2}$.
	Then we know that $\gamma_{r_1}$ must not be full dimensional \jessie{by argument from scoring rule $G$} and therefore, $\gamma_{r_1}$ must have empty interior.
	However, if $\gamma_{r_1} = \Gamma_{r_1}$ has empty interior, then $r_1\not\in \R'$, so we observe a contradiction.
	Thus, $\gamma$ is nonredundant.

	Therefore, our constructed $\gamma$ is nondegenerate, nonredundant, and $\gamma \preceq \Gamma$.
